Feeding Dynamic Behavior into Optimization: Simulation-based Multi-objective Overtime Planning

### 2014-09-03 data/result/Article/Latex/Article.tex
.

\begin{figure*}
\centering
\includegraphics[width=18cm, height=5cm]{boxplots2.pdf}
\caption{Box-plots for I$_{C}$ (left), I$_{HV}$ (middle) and I$_{GD}$ (right) quality indicators for NSGAII (box-plot), MAR ($\times$), SH ($\ast$), and CPM (+). The few solutions found under the second-half OMS are closer to optimal, though NSGAII produces a more diverse set of solutions.}
\end{figure*}

@@

% Table generated by Excel2LaTeX from sheet 'tabela 4'
\begin{table}[htbp]
	\scriptsize
  \centering
  \caption{Quality indicators for each instance under our approach (NSGAII) and a model without error dynamics (NSGA$_{NE}$). Pareto fronts for NSGA$_{NE}$ cover a larger part of the search space, leading to smaller $I_{GD}$. Solutions produced under NSGAII tend to concentrate in certain parts of the search space}
    \begin{tabular}{p{0.8cm}p{1.0cm}ccc}
    \toprule
    \textbf{Instance} & \textbf{Config.} & \textbf{I$_{C}$} & \textbf{I$_{HV}$} & \textbf{I$_{GD}$} \\
    \midrule
    \multirow{2}[2]{*}{ACAD} & NSGAII & 0.020 $\pm$ 0.022 & \textbf{0.464 $\pm$ 0.009} & 0.0066 $\pm$ 0.002 \\
          & NSGA$_{NE}$ & \textbf{0.020 $\pm$ 0.004} & 0.333 $\pm$ 0.001 & \textbf{0.0003 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{WMET} & NSGAII & 0.020 $\pm$ 0.019 & \textbf{0.492 $\pm$ 0.006} & 0.0037 $\pm$ 0.0 \\
          & NSGA$_{NE}$ & 0.020 $\pm$ 0.003 & 0.334 $\pm$ 0.001 & \textbf{0.0003 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{WAMS} & NSGAII & 0.020 $\pm$ 0.016 & \textbf{0.479 $\pm$ 0.004} & 0.0032 $\pm$ 0.0 \\
          & NSGA$_{NE}$ & 0.020 $\pm$ 0.003 & 0.337 $\pm$ 0.001 & \textbf{0.0002 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{PSOA} & NSGAII & 0.020 $\pm$ 0.014 & \textbf{0.421 $\pm$ 0.014} & 0.0129 $\pm$ 0.004 \\
          & NSGA$_{NE}$ & 0.020 $\pm$ 0.002 & 0.338 $\pm$ 0.001 & \textbf{0.0001 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{OMET} & NSGAII & 0.020 $\pm$ 0.014 & \textbf{0.465 $\pm$ 0.006} & 0.0044 $\pm$ 0.0 \\
          & NSGA$_{NE}$ & 0.020 $\pm$ 0.003 & 0.336 $\pm$ 0.001 & \textbf{0.0001 $\pm$ 0.0} \\\hline
    \multirow{2}[2]{*}{PARM} & NSGAII & 0.020 $\pm$ 0.019 & \textbf{0.489 $\pm$ 0.011} & 0.0090 $\pm$ 0.001 \\
          & NSGA$_{NE}$ & \textbf{0.020 $\pm$ 0.003} & 0.338 $\pm$ 0.001 & \textbf{0.0001 $\pm$ 0.0} \\
    \bottomrule
    \end{tabular}%
\end{table}%

% Table generated by Excel2LaTeX from sheet 'tabela 5'
\begin{table}[htbp]
  \scriptsize
	\centering
  \caption{Effect-sizes for comparisons between NSGAII and NSGA$_{NE}$}
    \begin{tabular}{lccc}
    \toprule
    \textbf{Instance} & \textbf{I$_{C}$} & \textbf{I$_{HV}$} & \textbf{I$_{GD}$} \\
    \midrule
    ACAD  & 38\%  & 100\% & 0\% \\
    WMET  & 40\%  & 100\% & 0\% \\
    WAMS  & 46\%  & 100\% & 0\% \\
    PSOA  & 50\%  & 100\% & 0\% \\
    OMET  & 43\%  & 100\% & 0\% \\
    PARM  & 38\%  & 100\% & 0\% \\
    \bottomrule
    \end{tabular}%
\end{table}%

@@

% Table generated by Excel2LaTeX from sheet 'tabela 6'
\begin{table}[htbp]
	\scriptsize
  \centering
  \caption{Average difference in makespan and cost for solutions involving excessive overtime for each instance. data shows that the formulation without overtime error dynamics tends to understimate both cost and makespan for most projects.}
    \begin{tabular}{rccc}
    \toprule
    \multicolumn{1}{c}{\multirow{2}[2]{*}{\textbf{Instance}}} & \multirow{2}[2]{*}{\textbf{Overtime  Range}} & \multicolumn{2}{c}{\textbf{(NSGA$_{NE}>$NSGAII)}} \\

    \multicolumn{1}{c}{} &       & \textbf{Makespan } & \textbf{Cost} \\
        \midrule
    \multicolumn{1}{l}{ACAD} & 332 - 376 hr & -2\%  & -1\% \\
    \multicolumn{1}{l}{WMET} & 332 - 372 hr & -4\%  & -3\% \\
    \multicolumn{1}{l}{WAMS} & 570 - 638 hr & -5\%  & -3\% \\
    \multicolumn{1}{l}{PSOA} & 1,288 - 1,443 hr & 6\%   & 5\% \\
    \multicolumn{1}{l}{OMET} & 919 - 1,023 hr & -6\%  & -4\% \\
    \multicolumn{1}{l}{PARM} & 797 - 884 hr & -5\%  & -3\% \\
    \bottomrule
    \end{tabular}%
\end{table}%

@@

\begin{figure*}
\centering
\includegraphics[scale=0.65]{2dplots.pdf}
\caption{2D projections for combinations of the number of overtime hours, makespan, and cost objectives for the smaller (ACAD) and largest (PARM) instances. The linear relations resulting from NSGA$_{NE}$ and the convex shape of NSGAII can be observed, as well as the few solutions provided by each OMS.}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=18cm, height=5cm]{boxplots2.pdf}
\caption{Box-plots for I$_{C}$ (left), I$_{HV}$ (middle) and I$_{GD}$ (right) quality indicators for NSGAII (box-plot), MAR ($\times$), SH ($\ast$), and CPM (+). The few solutions found under the second-half OMS are closer to optimal, though NSGAII produces a more diverse and closer to optimal set of solutions.}
\end{figure*}

@@

% Table generated by Excel2LaTeX from sheet 'tabela 4'
\begin{table}[htbp]
	\scriptsize
  \centering
  \caption{Quality indicators for each instance under our approach (NSGAII) and a model without error dynamics (NSGA$_{NE}$). Pareto fronts for NSGA$_{NE}$ cover a larger part of the solution space, leading to smaller $I_{GD}$. Solutions produced under NSGAII tend to concentrate in certain parts of the solution space}
    \begin{tabular}{p{0.8cm}p{1.0cm}ccc}
    \toprule
    \textbf{Instance} & \textbf{Config.} & \textbf{I$_{C}$} & \textbf{I$_{HV}$} & \textbf{I$_{GD}$} \\
    \midrule
    \multirow{2}[2]{*}{ACAD} 
				  & NSGAII      &         0.020 $\pm$ 0.011  & \textbf{0.530 $\pm$ 0.006} &         0.004 $\pm$ 0.001  \\
          & NSGA$_{NE}$ &         0.020 $\pm$ 0.004  &         0.333 $\pm$ 0.001  & \textbf{0.001 $\pm$ 0.00}  \\\hline
    \multirow{2}[2]{*}{WMET} 
				  & NSGAII      &         0.020 $\pm$ 0.012  & \textbf{0.544 $\pm$ 0.004} &         0.002 $\pm$ 0.001  \\
          & NSGA$_{NE}$ &         0.020 $\pm$ 0.003  &         0.334 $\pm$ 0.001  & \textbf{0.001 $\pm$ 0.000} \\\hline
    \multirow{2}[2]{*}{WAMS} 
				  & NSGAII      &         0.020 $\pm$ 0.010  & \textbf{0.498 $\pm$ 0.003} &         0.002 $\pm$ 0.001  \\
          & NSGA$_{NE}$ & \textbf{0.020 $\pm$ 0.003} &         0.337 $\pm$ 0.001  & \textbf{0.001 $\pm$ 0.000} \\\hline
    \multirow{2}[2]{*}{PSOA} 
				  & NSGAII      &         0.020 $\pm$ 0.011  & \textbf{0.471 $\pm$ 0.006} &         0.004 $\pm$ 0.001  \\
          & NSGA$_{NE}$ &         0.020 $\pm$ 0.002  &         0.338 $\pm$ 0.001  & \textbf{0.001 $\pm$ 0.000} \\\hline
    \multirow{2}[2]{*}{OMET} 
				  & NSGAII      &         0.020 $\pm$ 0.011  & \textbf{0.523 $\pm$ 0.004} &         0.002 $\pm$ 0.001  \\
          & NSGA$_{NE}$ &         0.020 $\pm$ 0.003  &         0.337 $\pm$ 0.001  & \textbf{0.001 $\pm$ 0.000} \\\hline
    \multirow{2}[2]{*}{PARM} 
				  & NSGAII      &         0.020 $\pm$ 0.018  & \textbf{0.462 $\pm$ 0.007} &         0.006 $\pm$ 0.001  \\
          & NSGA$_{NE}$ & \textbf{0.020 $\pm$ 0.003} &         0.338 $\pm$ 0.001  & \textbf{0.001 $\pm$ 0.000} \\
    \bottomrule
    \end{tabular}%
\end{table}%

% Table generated by Excel2LaTeX from sheet 'tabela 5'
\begin{table}[htbp]
  \scriptsize
	\centering
  \caption{Effect-sizes for comparisons between NSGAII and NSGA$_{NE}$}
    \begin{tabular}{lccc}
    \toprule
    \textbf{Instance} & \textbf{I$_{C}$} & \textbf{I$_{HV}$} & \textbf{I$_{GD}$} \\
    \midrule
    ACAD  &  42\%  & 100\% &   0\% \\
    WMET  &  44\%  & 100\% &   0\% \\
    WAMS  &  38\%  & 100\% &   0\% \\
    PSOA  &  42\%  & 100\% &   0\% \\
    OMET  &  44\%  & 100\% &   0\% \\
    PARM  &  43\%  & 100\% &   0\% \\
    \bottomrule
    \end{tabular}%
\end{table}%

@@

% Table generated by Excel2LaTeX from sheet 'tabela 6'
\begin{table}[htbp]
	\scriptsize
  \centering
  \caption{Average difference in makespan and cost for solutions involving excessive overtime for each instance. data shows that the formulation without overtime error dynamics tends to understimate both cost and makespan for most projects}
    \begin{tabular}{rccc}
    \toprule
    \multicolumn{1}{c}{\multirow{2}[2]{*}{\textbf{Instance}}} & \multirow{2}[2]{*}{\textbf{Overtime  Range}} & \multicolumn{2}{c}{\textbf{(NSGA$_{NE}>$NSGAII)}} \\

    \multicolumn{1}{c}{} &       & \textbf{Makespan } & \textbf{Cost} \\
        \midrule
    \multicolumn{1}{l}{ACAD} &   334 -   374 hr & -5.2\% & -3.6\% \\
    \multicolumn{1}{l}{WMET} &   374 -   414 hr & -8.4\% & -6.4\% \\
    \multicolumn{1}{l}{WAMS} &   638 -   705 hr & -8.5\% & -5.9\% \\
    \multicolumn{1}{l}{PSOA} & 1,445 - 1,599 hr & -4.5\% & -2.6\% \\
    \multicolumn{1}{l}{OMET} & 1,042 - 1,148 hr & -9.2\% & -6.9\% \\
    \multicolumn{1}{l}{PARM} &   792 -   882 hr & -7.3\% & -5.5\% \\
    \bottomrule
    \end{tabular}%
\end{table}%

@@

\begin{figure*}
\centering
\includegraphics[scale=0.65]{2dplots2.pdf}
\caption{2D projections for combinations of the number of overtime hours, makespan, and cost objectives for the smaller (ACAD) and largest (PARM) instances. The linear relations resulting from NSGA$_{NE}$ and the convex shape of NSGAII can be observed, as well as the few solutions provided by each OMS.}
\end{figure*}
